---
title: "DDS_LiveSessionAssignment_U5 - Functions in R"
author: "Najeeb Zaidi"
date: "July 30, 2016"
output: html_document
---
# Introduction
The functions created in this exercise allow conversion from one base to another. 
For record, R Studio (v3.3.0) sessionInfo is listed in the notes section.

## Item 1: A function called P7 which takes one argument n, and will return (or print) the first n numbers in base 7:

```{r include = FALSE, echo = FALSE}
#Set your desired work directory
getwd()  
setwd("C:/Users/najee/Documents/R/MSDS6306-W5-LS")

# Prelim. / Code prep.
rm(list = ls()) 
objects()
```

```{r echo = FALSE}
P7 <- function(n, base = 7) 
{
  if (n == 0) 
    return(c())
  if (n < 0) 
    stop(simpleError("Negative number can???t be used with this function"))
  nDigits <- ceiling(log(n + 1, 7))
  powers <- 7 ^ (0:nDigits)
  out <- diff(n %% powers)/powers[-length(powers)]
  out1 <- rev(out)
  out2 <- paste(out1, collapse = '')
  out2 = as.numeric(out2)
  out3 <- 1:out2
  return(out3)
}
# To use the function, just simple enter the integer desired (n) and it will 
# return the series of the first (n) integer up to the (n) correspondent
# number # in base 7. The functions also checks for null and negative values. # For example:  
P7(5)
```
##  Question 2. Write a function called ???base10to7??? which takes one argument x, and will convert a decimal number to base 7.

```{r}
Base10to7 <- function(n, base = 7) 
{ 
  if (n == 0) 
    return(c())
  if (n < 0) 
    stop(simpleError("Negative number can???t be used with this function"))
  
##  if ( is.scalar(n) == FALSE) 
##    stop(simpleError("Please use scalar numbers"))
  nDigits <- ceiling(log(n + 1, 7))
  powers <- 7 ^ (0:nDigits)
  out <- diff(n %% powers)/powers[-length(powers)]
  return(rev(out))
}
Base10to7(25)
```


## Question 3. Write a function called ???base7to10??? which takes an argument y, and converts a base number 7 to decimal. 

```{r}
Base7to10 = function(base_number, base = 7) 
  {
  split_base = strsplit(as.character(base_number), split = "")
  return(sapply(split_base, function(x) sum(as.numeric(x) * base ^ (rev(seq_along(x) - 1)))))
  }

# To use the function, just simple enter the desired integer (to be considered in base 7) and it will return the correspondent number in base 10. For example: 
Base7to10(5)
```
## Question 4: generalize the function to take any form & especially steps 1 2 , 3 above:

```{r echo = FALSE}
numberInBase <- function(number,base)
  {
  numberInBaseRecur <- function(number,base)
    {
    lastDigit <- function(number,base) number %% base
    if (number == 0) result <- c(0)
    else result <- c(numberInBaseRecur(number %/% base,base),
                     lastDigit(number,base))
    result
    }
  result <- numberInBaseRecur(number,base)
  while (result[1] == 0 && length(result) > 1) result <- result[-1]
  result
  }
use <- function(digiseq)
  {
  digits <- c(as.character(0:9),LETTERS)
  paste(sapply(digiseq,function(x)digits[x + 1]),collapse = "")
  }
use(numberInBase(21,2))

# To use the function use(numberInBase(m,n), just simple enter a desired integer as first parameter and the desired base value as second parameter and the function will return the input m number in the selected base n. For example:  
use(numberInBase(21,2)) # will give you [1] "10101"
use(numberInBase(30,8)) # will give you [1] "36"
use(numberInBase(556,10)) # will give you [1] "556"
use(numberInBase(556,16)) # will give you [1] "22C"

```
## Question 5: Plot a bar or histogram chart for each
 As an example, we are using here the functions use(numberInBase(m,n)) to plot a chart with 2 numbers, the first one being the inputed number m (assumed in base 10) and the second one its equivalent in base n

```{r}
m <- 167
n <- 8
c <- use(numberInBase(m , n)) # This returns 247 as the equivalent of 167 (b10) in base 8
v <- c(m , c)
v1 <- as.numeric(v)

# using additional arguments to customize a graphic
v1LabelMain <- "Correspondent numbers in different scale"
v1LabelX <- "Numbers"
v1LabelY <- "Values"
v1RainbowColors <- rainbow(length(v1))
# Y axis range could be adjusted like this: ylim<-max(v1) + v1LimY <- c(0, ylim) as well as other customizations are possible ie showing legend, values, adding text, dividing the chart in panels, etc. ???
barplot(height = v1, main = v1LabelMain, xlab = v1LabelX, ylab = v1LabelY, ylim = c(0,300), col = v1RainbowColors)

```
## aaa

```{r}
# Question 6: plot a histogram for density function Pr(5<X<15) and the uniform distribution is (0, 30)
# Can we generalize this function plot?
# Let's draw a sample of size 1000 from a normal distribution with mean 0 and standard deviation 30 

x <- rnorm(1000, 0, 30)
m = mean(x)
s = sd(x)
hist(x, col = "#d3d3d3", probability = TRUE, main = "Histograms and density function for a rand (0,30) sample")

# Adding vertical lines to capture 95% of the sample
lines(c(-s*1.96,-s*1.96), c(0, dnorm(-s*1.96)), col = "green")
lines(c(s*1.96,s*1.96), c(0, dnorm(s*1.96)), col = "green")

# Adding the distribution curve with parameters m and s 
curve(dnorm(x, mean = m, sd = s), col = "red", add = TRUE)
# Adding the probability density curve  
lines(density(x), col = "black")

```

## References :
It would be possible to generalize the function plot. For further references:
 
     * https://cran.r-project.org/web/packages/ggfortify/vignettes/plot_dist.html 
     * https://tomizonor.wordpress.com/2013/05/11/distribution-density-histogram/
     * http://nicercode.github.io/guides/plotting/

### Notes: 
A. Question numbers in this exercise were relabelled because the originial Q1 was not clearly worded nor the associated diagram spelled the requirement.

B. 
```{r, echo=TRUE}
sessionInfo()


```




